How do agents form inflation expectations? evidences from cross-moment estimation and the uncertainty

### 2020-04-12 paper/InfVar.tex
a rough draft before the submission to Oxford Phd macro.

	\begin{abstract}
	Density forecasts of macroeconomic variables provide one additional moment restriction, uncertainty, for testing and exploring the implications of theories about how people form expectations differently from full-information rationality benchmark. This paper first documents the persistent dispersion in inflation uncertainty of professionals and households, and how it conveys different information from the widely used proxies to uncertainty such as cross-sectional disagreement and forecast errors. Second, utilizing the panel data structure of both surveys, I provide additional reduced-form test results as well as structural estimates for each particular theory of ``irrational expectation'' by jointly accounting for its predictions for different moments. This is a natural extension of \citet{coibion2012can}, which examines different moments separately. Also, motivated by the time-varying pattern of the uncertainty observed from surveys, I extend their work to allow for an alternative inflation process featuring stochastic volatility. These extensions allow me to match the joint dynamics of inflation and forecast moments in a better degree of fitness. It also illustrates how incorporating higher moments from survey data helps understand both the expectation formation mechanisms and inflation dynamics.   
	\end{abstract}

@@

	\begin{table}[ht]
		\centering
		\caption{Definition and Notation of Moments}
		\label{MomSum}
		\begin{tabular}{ll}

@@

	\begin{figure}[ht]
		\centering
		\includegraphics[width=13cm]{figures/ni_illustration.png}  \\
		\begin{flushleft}
		{\footnotesize Note: the top two figures plot the nowcasting of $y_{t+k}$  at time $t+k$ and forecasting of $y_{t+h}$ at time $t+k$ through Kalman filtering and through FIRE after a one-time shock of size of one unit at time $t$. The nowcasting and forecasting uncertainty are correspondingly plotted in the bottom. Both private signal and public signal have the conditional variance equal to long-run variance of y, i.e.  $\sigma_\epsilon = \sigma_\xi = \sigma_y$. The plotted signals are are a pair of particular draw from their respective conditional distribution. }
		\end{flushleft}
		\caption{Nowcasting and Forecasting in Noisy Information}
		\label{IllustrateNI}
	\end{figure}

@@

	\begin{figure}[ht]
		\centering
		\includegraphics[width=\textwidth]{figures/ir_popseni.png} 
		\begin{flushleft}
			{\footnotesize Note: figure 1-6 plot the dynamics of a one-time shock to inflation $\omega_{t+k}$, the realized value of $y_{t+k}$,  average forecast of $\bar y_{t+10|t+k}$, forecasting errors $\overline{FE}_{t+10|t+k}$, disagreements $\overline {Disg}_{t+10|t+k}$, and uncertainty $\bar \sigma^2_{t+10|t+k}$ to a one-time shock  of unit one at time $t$, i.e. $\omega_t=1$. For NI, public and private signals’ variance is equal to long-run variance of $y$, i.e. $\sigma_\epsilon = \sigma_\xi = \sigma_\xi $. For SE, $\lambda = 0.25$.  }
		\end{flushleft}
		\caption{Impulse responses of population moments to a shock to inflation}
		\label{ir_pop}
	\end{figure}

@@

	\begin{figure}[ht]
		\centering
		\includegraphics[width=0.7\textwidth]{figures/rigidity.png} 
		\begin{flushleft}
			{\footnotesize Note: implied rigidity is $1-\lambda$ in SE and $(1-P_{t+k}H)$ in NI. Rigidity from NI are plotted for three values of noisiness of signals, i.e. 0.1, 1 and 10 times of the unconditional variance of $y$. }
		\end{flushleft}
		\caption{Rigidity from Two Models}
		\label{rigidity}
	\end{figure}

@@

	\begin{table}[ht]
		\caption{Information of Data}
		\label{DataInfo}
		\begin{tabularx}{\textwidth}{|X|X|X|}
			\hline 
			& SCE & SPF        \\
			\hline 
			Time period                                    & 2013-2019                           &
			 2007-2019             \\
			 \hline 
			Frequency                                      & Monthly                                 & Quarterly                \\
			\hline 
			Sample Size                                    & 1,300                                   & 30-50                    \\
			\hline 
			Var in Density                       & 1-yr and 2-yr-ahead inflation          & 1-yr-ahead GDP deflator, Core CPI and Core PCE         \\
			\hline 
			Panel Structure                               & stay up to 12 months                    & average stay for 5 years \\
			\hline 
			Individual Info                        & Education, Income, Age, Location        & Industry    \\
			\hline 
		\end{tabularx}
	\end{table}

@@

	\begin{figure}[ht]
		\centering
		\begin{subfigure}[b]{\textwidth}
			\centering
			\caption{Realized Inflation and Uncertainty}
			\label{InfVar}
			\includegraphics[width=0.3\textwidth]{figures/Inf1yf_CPICore_varSPFCPIQ.png}
			\includegraphics[width=0.3\textwidth]{figures/Inf1yf_PCECore_varSPFPCEQ.png}
			\includegraphics[width=0.3\textwidth]{figures/Inf1yf_CPIAU_varSCEM.png}
		\end{subfigure}
	    \vspace{1em}
		\vfill
		\begin{subfigure}[b]{\textwidth}
			\centering
			\caption{Size of Forecast Errors and Uncertainty}
			\label{FEVar}
			\includegraphics[width=0.3\textwidth]{figures/SPFCPI_abFE_varSPFCPIQ.png}
			\includegraphics[width=0.3\textwidth]{figures/SPFPCE_abFE_varSPFPCEQ.png}
			\includegraphics[width=0.3\textwidth]{figures/SCE_abFE_varSCEM.png}
		\end{subfigure}
	 \vspace{0.5em}
		\vfill
		\begin{subfigure}[b]{\textwidth}
			\centering
			\caption{Disagreement and Uncertainty}
			\label{DisgVar}
			\includegraphics[width=0.3\textwidth]{figures/CORECPI_disg_varSPFCPIQ.png}
			\includegraphics[width=0.3\textwidth]{figures/COREPCE_disg_varSPFPCEQ.png}
			\includegraphics[width=0.3\textwidth]{figures/Q9_disg_varSCEM.png}\\
		\end{subfigure}
		\\
		\begin{flushleft}
			{\footnotesize Note:  From left to right: SPF's  forecasts of core CPI and core PCE, and SCE's forecast of headline CPI. From top to the bottom, uncertainty (red dash) versus realized inflation (blue dot) with correlation coefficient of 0.14, 0.12 and -0.25, respectively; uncertainty (red dash) versus absolute value of forecast errors (blue dot) with correlation coefficient of -0.19, -0.18, 0.27, respectively; uncertainty (red dash) versus  disagreements (blue dot) with correlation coefficient of -0.31, -0.37 and 0.43,repectively. Only the Pearson tests of correlation between disagreement and uncertainty are significant for all.}
		\end{flushleft}
		\caption{Uncertainty and Other Moments}
	\end{figure}

	\begin{figure}[ht]
		\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\caption{Mean Forecasts}
		\includegraphics[width=7cm]{figures/IQRmeanCPIQ.png} 
		\smallskip
		\includegraphics[width=7cm]{figures/IQRmeanPCEQ.png}
		\smallskip
		\includegraphics[width=7cm]{figures/IQRmeanSCEM.png}
		\end{subfigure}
	    \hfill 
		\begin{subfigure}[b]{0.5\textwidth}
		\centering 
		\caption{Uncertainty}
		\includegraphics[width=7cm]{figures/IQRvarCPIQ.png}
		\smallskip
		\includegraphics[width=7cm]{figures/IQRvarPCEQ.png}
		\smallskip
		\includegraphics[width=7cm]{figures/IQRvarSCEM.png}
		\end{subfigure}
		\caption{Dispersion of Mean Forecasts and Unceratinty }
		\label{IQR_Unceratitny}
	\end{figure}

	\begin{figure}[ht]
		\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\caption{Mean Forecasts}
		\includegraphics[width=7cm]{figures/PRCCPIMean1_hist.png} 
		\smallskip
		\includegraphics[width=7cm]{figures/PRCPCEMean1_hist.png} 
		\smallskip
		\includegraphics[width=7cm]{figures/SCEmean_hist.png} 
		\end{subfigure}
	   \hfill 
	  	\begin{subfigure}[b]{0.5\textwidth}
	  	\caption{Uncertainty}
		\includegraphics[width=7cm]{figures/PRCCPIVar1_hist.png}  
		\smallskip
		\includegraphics[width=7cm]{figures/PRCPCEVar1_hist.png}  
		\smallskip
		\includegraphics[width=7cm]{figures/SCEvar_hist.png}  
		\end{subfigure}
		\caption{Distribution of Mean Forecast and Uncertainty }
		\label{Unceratitny_Histogram}
	\end{figure}

	\begin{figure}[ht]
		\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\caption{Revision in Mean Forecasts}
		\includegraphics[width=7cm]{figures/PRCCPIMean01_rv_true_hist.png} 
		\smallskip
		\includegraphics[width=7cm]{figures/PRCPCEMean01_rv_true_hist.png} 
		\end{subfigure}
		   \hfill 
		\begin{subfigure}[b]{0.5\textwidth}
					\caption{Revision in Uncertainty}
		\includegraphics[width=7cm]{figures/PRCCPIVar01_rv_true_hist.png}  
		\smallskip
		\includegraphics[width=7cm]{figures/PRCPCEVar01_rv_true_hist.png} 
		\end{subfigure}
		\caption{Distribution of Revision in Forecasts and Uncertainty}
		\label{RevisionHist}
	\end{figure}

@@

	\begin{table}[ht]
		\caption{Tests of Rationality and Efficiency Using Forecast Errors}
		\label{NullTestTable}
		\centering 
		\begin{tabular}{llll}
			\hline 
			& SPF CPI          & SPF PCE          & SCE            \\
			\hline 
			\multicolumn{4}{l}{Test 1: Unbiasedness}                                                           \\
			\hline 
			Constant                            & 0.122***         & 0.586***         & 2.220***       \\
			& (0.017)          & (0.061)          & (0.019)        \\
			\hline 
			N                                   & 4697             & 1208             & 67380          \\
			\hline 
			\multicolumn{4}{l}{Test 2: FE does not depend on past information}                                  \\
			\hline 
			Forecast 1-yr before                & 0.307***         & 0.586***         & NA             \\
			& (0.020)          & (0.061)          & NA             \\
			Constant                            & -0.655***        & -0.777***        & NA             \\
			& (0.060)          & (0.116)          & NA             \\
			\hline 
			N                                   & 3429             & 1208             & NA             \\
			$R^2$                 & 0.0721           & 0.118            & NA             \\
			\hline 
			\multicolumn{4}{l}{Test 3: FEs of non-overlapping forecast horizons not serially correlated} \\
			\hline 
			Forecast Error 1-year before        & 0.0756***        & 0.0503***        & NA             \\
			& (0.020)          & (0.035)          & NA             \\
			Constant                            & 0.145***         & 0.275***         & NA             \\
			& (0.021)          & (0.035)          & NA             \\
			\hline 
			N                                   & 3356             & 1208             & NA             \\
			$R^2$                   & 0.00591          & 0.00264          & NA             \\
			\hline 
			\multicolumn{4}{l}{Test 4: Overlapping FEs are only weakly serially correlated}                          \\
			\hline 
			Forecast Error 1-q before           & 0.657***         & 0.834***         & 0.297***       \\
			& (0.025)          & (0.037)          & (0.021)        \\
			Forecast Error 2-q before           & 0.0282           & -0.0858          & 0.308***       \\
			& (0.027)          & (0.048)          & (0.046)        \\
			Forecast Error 3-q before           & -0.0244          & -0.0555          & 0.311***       \\
			& (0.025)          & (0.038)          & (0.045)        \\
			Constant                            & 0.0626***        & 0.113***         & 0.742***       \\
			& (0.019)          & (0.026)          & (0.097)        \\
			\hline 
			N                                   & 2536             & 1004             & 2836           \\
			$R^2$                & 0.439            & 0.552            & 0.232    \\
			\hline      
		\end{tabular}
	\\
	{\footnotesize Note: white standard errors reported in the parentheses of estimations.  *** p$<$0.001, ** p$<$0.01 and * p$<$0.05. }

@@

		\begin{sidewaystable}[ht]

@@

	\begin{sidewaystable}[ht]
		\begin{adjustbox}{width={24cm},totalheight={14cm}}
			\begin{threeparttable}
				\caption{Weak Tests of Revision Efficiency Using Change in Forecasts and Uncertainty}
				\label{WeakRevEfficiency}
				\begin{tabular}{llllllllllllll}
					\hline 
					& \multicolumn{4}{l}{SPF CPI}                     & \multicolumn{4}{l}{SPF PCE}                       &                      & \multicolumn{4}{l}{SCE}                           \\
					\hline 
					\multicolumn{14}{l}{Test 3. Weak revision efficiency of change in forecast}                                                                                                                                    \\
					\hline 
					& Mean change & t-1       & t-1- t-2  & t-1-t-3   & Mean revision & t-1       & t-1- t-2  & t-1-t-3   &                      & Mean revision & t-1       & t-1- t-2  & t-1-t-3   \\
					\hline 
					L.InfExp\_Mean\_ch   &             & -0.295*** & -0.344*** & -0.367*** &               & -0.303*** & -0.348*** & -0.364*** & L.InfExp\_Mean\_ch  &         & -0.433*** & -0.586*** & -0.642*** \\
					&             & (0.034)   & (0.044)   & (0.045)   &               & (0.043)   & (0.059)   & (0.062)   &                    &         & (0.01)     & (0.013)    & (0.025)    \\

@@

	\begin{figure}[ht]
		\centering
		\includegraphics[width=0.8\textwidth,totalheight=0.6\textwidth]{figures/inf_shocksQ.png}
			\begin{flushleft}
			{\footnotesize Note: all the shocks are normalized by their sample standard deviation. Technology shock is idetified by long-run restriction of structural VAR with labor productivity, hours and inflation. Oil shock is defined as the max \{0, the largest increase of oil price over the past 12 months.\} }
		\end{flushleft}
		\caption{ Shocks to Inflation}
		\label{Inflationshocks}
	\end{figure}

@@

\begin{figure}[ht]
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\caption{Technology and Oil Shocks}
		\includegraphics[width=7cm]{figures/CPIAU_ashocks_nmp_before2007.png}  
		\smallskip
		\includegraphics[width=7cm]{figures/SPFFE_ashocks_nmp_before2007.png} 
		\smallskip
		\includegraphics[width=7cm]{figures/SPFDisg_ab_ashocks_nmp_before2007.png} 
	\end{subfigure}
	\hspace{1em}
	\hfill
	\begin{subfigure}[b]{0.5\textwidth}
		\caption{Monetary Policy Shocks}
		\includegraphics[width=7cm]{figures/CPIAU_ashocks_before2007.png} 
		\smallskip
		\includegraphics[width=7cm]{figures/SPFFE_ashocks_before2007.png} 
		\smallskip
		\includegraphics[width=7cm]{figures/SPFDisg_ab_ashocks_before2007.png} 
	\end{subfigure}
	\caption{Responses of Inflation and Professional Forecast Moments: 1984-2007}
	\label{ReplicateCoibionBefore2007}
\end{figure}

@@

		\begin{figure}[ht]
		\begin{subfigure}[b]{0.5\textwidth}
			\centering
			\caption{Technology and Oil Shocks}
			\includegraphics[width=7cm]{figures/Inf_ashocks_nmp.png}  
			\smallskip
			\includegraphics[width=7cm]{figures/SPFFE_ashocks_nmp.png} 
			\smallskip 
			\includegraphics[width=7cm]{figures/SPFDisg_ab_ashocks_nmp.png} 
			\smallskip 
			\includegraphics[width=7cm]{figures/SPFVar_ab_ashocks_nmp.png} 
		\end{subfigure}
		\hfill
		\hspace{1em}
		\begin{subfigure}[b]{0.5\textwidth}
			\caption{Monetary Policy Shocks}
			\includegraphics[width=7cm]{figures/Inf_ashocks.png} 
			\smallskip
			\includegraphics[width=7cm]{figures/SPFFE_ashocks.png} 
			\smallskip
			\includegraphics[width=7cm]{figures/SPFDisg_ab_ashocks.png} 
			\smallskip
			\includegraphics[width=7cm]{figures/SPFVar_ab_ashocks.png} 
		\end{subfigure} 
		\caption{Responses of Inflation and Professional Forecast Moments: 1984-2019}
		\label{ReplicateCoibionwholeperiod}
	\end{figure}

@@

	\begin{figure}[ht]

@@

\subsection{Moments matching and parameter estimates}

\subsection{The scoring card of different theories}

>>>>

	\begin{abstract}
	Density forecasts of macroeconomic variables provide one additional moment restriction, uncertainty, for testing and exploring the implications of theories about how people form expectations differently from full-information rationality benchmark. This paper first documents the persistent dispersion in inflation uncertainty of professionals and households, and how it conveys different information from the widely used proxies to uncertainty such as cross-sectional disagreement and forecast errors. Second, utilizing the panel data structure of both surveys, I provide additional reduced-form test results as well as structural estimates for each particular theory of ``irrational expectation'' by jointly accounting for its predictions for different moments. This is a natural extension of \citet{coibion2012can}, which examines different moments separately. Also, motivated by the time-varying pattern of the uncertainty observed from surveys, I extend their work to allow for an alternative inflation process featuring stochastic volatility. These extensions allow me to match the joint dynamics of inflation and forecast moments in better goodness of fit. It also testifies how incorporating higher moments from survey data helps understand both the expectation formation mechanisms and inflation dynamics.   
	\end{abstract}

@@

	\begin{table}[p]
		\centering
		\caption{Definition and Notation of Moments}
		\label{MomSum}
		\begin{tabular}{ll}

@@

	\begin{figure}[p]
		\centering
		\includegraphics[width=13cm]{figures/ni_illustration.png}  \\
		\begin{flushleft}
		{\footnotesize Note: the top two figures plot the nowcasting of $y_{t+k}$  at time $t+k$ and forecasting of $y_{t+h}$ at time $t+k$ through Kalman filtering and through FIRE after a one-time shock of size of one unit at time $t$. The nowcasting and forecasting uncertainty are correspondingly plotted in the bottom. Both private signal and public signal have the conditional variance equal to long-run variance of y, i.e.  $\sigma_\epsilon = \sigma_\xi = \sigma_y$. The plotted signals are are a pair of particular draw from their respective conditional distribution. }
		\end{flushleft}
		\caption{Nowcasting and Forecasting in Noisy Information}
		\label{IllustrateNI}
	\end{figure}

@@

	\begin{figure}[p]
		\centering
		\includegraphics[width=\textwidth]{figures/ir_popseni.png} 
		\begin{flushleft}
			{\footnotesize Note: figure 1-6 plot the dynamics of a one-time shock to inflation $\omega_{t+k}$, the realized value of $y_{t+k}$,  average forecast of $\bar y_{t+10|t+k}$, forecasting errors $\overline{FE}_{t+10|t+k}$, disagreements $\overline {Disg}_{t+10|t+k}$, and uncertainty $\bar \sigma^2_{t+10|t+k}$ to a one-time shock  of unit one at time $t$, i.e. $\omega_t=1$. For NI, public and private signals’ variance is equal to long-run variance of $y$, i.e. $\sigma_\epsilon = \sigma_\xi = \sigma_\xi $. For SE, $\lambda = 0.25$.  }
		\end{flushleft}
		\caption{Impulse responses of population moments to a shock to inflation}
		\label{ir_pop}
	\end{figure}

@@

	\begin{figure}[p]
		\centering
		\includegraphics[width=0.7\textwidth]{figures/rigidity.png} 
		\begin{flushleft}
			{\footnotesize Note: implied rigidity is $1-\lambda$ in SE and $(1-P_{t+k}H)$ in NI. Rigidity from NI are plotted for three values of noisiness of signals, i.e. 0.1, 1 and 10 times of the unconditional variance of $y$. }
		\end{flushleft}
		\caption{Rigidity from Two Models}
		\label{rigidity}
	\end{figure}

@@

	\begin{table}[p]
		\caption{Information of Data}
		\label{DataInfo}
		\begin{tabularx}{\textwidth}{|X|X|X|}
			\hline 
			& SCE & SPF        \\
			\hline 
			Time period                                    & 2013-2019                           &
			 2007-2019             \\
			 \hline 
			Frequency                                      & Monthly                                 & Quarterly                \\
			\hline 
			Sample Size                                    & 1,300                                   & 30-50                    \\
			\hline 
			Var in Density                       & 1-yr and 2-yr-ahead inflation          & 1-yr-ahead GDP deflator, Core CPI and Core PCE         \\
			\hline 
			Panel Structure                               & stay up to 12 months                    & average stay for 5 years \\
			\hline 
			Individual Info                        & Education, Income, Age, Location        & Industry    \\
			\hline 
		\end{tabularx}
	\end{table}

@@

	\begin{figure}[p]
		\centering
		\begin{subfigure}[b]{\textwidth}
			\centering
			\caption{Realized Inflation and Uncertainty}
			\label{InfVar}
			\includegraphics[width=0.3\textwidth]{figures/Inf1yf_CPICore_varSPFCPIQ.png}
			\includegraphics[width=0.3\textwidth]{figures/Inf1yf_PCECore_varSPFPCEQ.png}
			\includegraphics[width=0.3\textwidth]{figures/Inf1yf_CPIAU_varSCEM.png}
		\end{subfigure}
	    \vspace{1em}
		\vfill
		\begin{subfigure}[b]{\textwidth}
			\centering
			\caption{Size of Forecast Errors and Uncertainty}
			\label{FEVar}
			\includegraphics[width=0.3\textwidth]{figures/SPFCPI_abFE_varSPFCPIQ.png}
			\includegraphics[width=0.3\textwidth]{figures/SPFPCE_abFE_varSPFPCEQ.png}
			\includegraphics[width=0.3\textwidth]{figures/SCE_abFE_varSCEM.png}
		\end{subfigure}
	 \vspace{0.5em}
		\vfill
		\begin{subfigure}[b]{\textwidth}
			\centering
			\caption{Disagreement and Uncertainty}
			\label{DisgVar}
			\includegraphics[width=0.3\textwidth]{figures/CORECPI_disg_varSPFCPIQ.png}
			\includegraphics[width=0.3\textwidth]{figures/COREPCE_disg_varSPFPCEQ.png}
			\includegraphics[width=0.3\textwidth]{figures/Q9_disg_varSCEM.png}\\
		\end{subfigure}
		\\
		\begin{flushleft}
			{\footnotesize Note:  From left to right: SPF's  forecasts of core CPI and core PCE, and SCE's forecast of headline CPI. From top to the bottom, uncertainty (red dash) versus realized inflation (blue dot) with correlation coefficient of 0.14, 0.12 and -0.25, respectively; uncertainty (red dash) versus absolute value of forecast errors (blue dot) with correlation coefficient of -0.19, -0.18, 0.27, respectively; uncertainty (red dash) versus  disagreements (blue dot) with correlation coefficient of -0.31, -0.37 and 0.43,repectively. Only the Pearson tests of correlation between disagreement and uncertainty are significant for all.}
		\end{flushleft}
		\caption{Uncertainty and Other Moments}
	\end{figure}

	\begin{figure}[p]
		\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\caption{Mean Forecasts}
		\includegraphics[width=7cm]{figures/IQRmeanCPIQ.png} 
		\smallskip
		\includegraphics[width=7cm]{figures/IQRmeanPCEQ.png}
		\smallskip
		\includegraphics[width=7cm]{figures/IQRmeanSCEM.png}
		\end{subfigure}
	    \hfill 
		\begin{subfigure}[b]{0.5\textwidth}
		\centering 
		\caption{Uncertainty}
		\includegraphics[width=7cm]{figures/IQRvarCPIQ.png}
		\smallskip
		\includegraphics[width=7cm]{figures/IQRvarPCEQ.png}
		\smallskip
		\includegraphics[width=7cm]{figures/IQRvarSCEM.png}
		\end{subfigure}
		\caption{Dispersion of Mean Forecasts and Unceratinty }
		\label{IQR_Unceratitny}
	\end{figure}

	\begin{figure}[p]
		\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\caption{Mean Forecasts}
		\includegraphics[width=7cm]{figures/PRCCPIMean1_hist.png} 
		\smallskip
		\includegraphics[width=7cm]{figures/PRCPCEMean1_hist.png} 
		\smallskip
		\includegraphics[width=7cm]{figures/SCEmean_hist.png} 
		\end{subfigure}
	   \hfill 
	  	\begin{subfigure}[b]{0.5\textwidth}
	  	\caption{Uncertainty}
		\includegraphics[width=7cm]{figures/PRCCPIVar1_hist.png}  
		\smallskip
		\includegraphics[width=7cm]{figures/PRCPCEVar1_hist.png}  
		\smallskip
		\includegraphics[width=7cm]{figures/SCEvar_hist.png}  
		\end{subfigure}
		\caption{Distribution of Mean Forecast and Uncertainty }
		\label{Unceratitny_Histogram}
	\end{figure}

	\begin{figure}[p]
		\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\caption{Revision in Mean Forecasts}
		\includegraphics[width=7cm]{figures/PRCCPIMean01_rv_true_hist.png} 
		\smallskip
		\includegraphics[width=7cm]{figures/PRCPCEMean01_rv_true_hist.png} 
		\end{subfigure}
		   \hfill 
		\begin{subfigure}[b]{0.5\textwidth}
					\caption{Revision in Uncertainty}
		\includegraphics[width=7cm]{figures/PRCCPIVar01_rv_true_hist.png}  
		\smallskip
		\includegraphics[width=7cm]{figures/PRCPCEVar01_rv_true_hist.png} 
		\end{subfigure}
		\caption{Distribution of Revision in Forecasts and Uncertainty}
		\label{RevisionHist}
	\end{figure}

@@

	\begin{table}[p]
		\caption{Tests of Rationality and Efficiency Using Forecast Errors}
		\label{NullTestTable}
		\centering 
		\begin{tabular}{llll}
			\hline 
			& SPF CPI          & SPF PCE          & SCE            \\
			\hline 
			\multicolumn{4}{l}{Test 1: Unbiasedness}                                                           \\
			\hline 
			Constant                            & 0.122***         & 0.586***         & 2.220***       \\
			& (0.017)          & (0.061)          & (0.019)        \\
			\hline 
			N                                   & 4697             & 1208             & 67380          \\
			\hline 
			\multicolumn{4}{l}{Test 2: FE does not depend on past information}                                  \\
			\hline 
			Forecast 1-yr before                & 0.307***         & 0.586***         & NA             \\
			& (0.020)          & (0.061)          & NA             \\
			Constant                            & -0.655***        & -0.777***        & NA             \\
			& (0.060)          & (0.116)          & NA             \\
			\hline 
			N                                   & 3429             & 1208             & NA             \\
			$R^2$                 & 0.0721           & 0.118            & NA             \\
			\hline 
			\multicolumn{4}{l}{Test 3: FEs of non-overlapping forecast horizons not serially correlated} \\
			\hline 
			Forecast Error 1-year before        & 0.0756***        & 0.0503***        & NA             \\
			& (0.020)          & (0.035)          & NA             \\
			Constant                            & 0.145***         & 0.275***         & NA             \\
			& (0.021)          & (0.035)          & NA             \\
			\hline 
			N                                   & 3356             & 1208             & NA             \\
			$R^2$                   & 0.00591          & 0.00264          & NA             \\
			\hline 
			\multicolumn{4}{l}{Test 4: Overlapping FEs are only weakly serially correlated}                          \\
			\hline 
			Forecast Error 1-q before           & 0.657***         & 0.834***         & 0.297***       \\
			& (0.025)          & (0.037)          & (0.021)        \\
			Forecast Error 2-q before           & 0.0282           & -0.0858          & 0.308***       \\
			& (0.027)          & (0.048)          & (0.046)        \\
			Forecast Error 3-q before           & -0.0244          & -0.0555          & 0.311***       \\
			& (0.025)          & (0.038)          & (0.045)        \\
			Constant                            & 0.0626***        & 0.113***         & 0.742***       \\
			& (0.019)          & (0.026)          & (0.097)        \\
			\hline 
			N                                   & 2536             & 1004             & 2836           \\
			$R^2$                & 0.439            & 0.552            & 0.232    \\
			\hline      
		\end{tabular}
	\\
	{\footnotesize Note: white standard errors reported in the parentheses of estimations.  *** p$<$0.001, ** p$<$0.01 and * p$<$0.05. }

@@

		\begin{sidewaystable}[p]

@@

	\begin{sidewaystable}[p]
		\begin{adjustbox}{width={24cm},totalheight={14cm}}
			\begin{threeparttable}
				\caption{Weak Tests of Revision Efficiency Using Change in Forecasts and Uncertainty}
				\label{WeakRevEfficiency}
				\begin{tabular}{llllllllllllll}
					\hline 
					& \multicolumn{4}{l}{SPF CPI}                     & \multicolumn{4}{l}{SPF PCE}                       &                      & \multicolumn{4}{l}{SCE}                           \\
					\hline 
					\multicolumn{14}{l}{Test 3. Weak revision efficiency of change in forecast}                                                                                                                                    \\
					\hline 
					& Mean change & t-1       & t-1- t-2  & t-1-t-3   & Mean revision & t-1       & t-1- t-2  & t-1-t-3   &                      & Mean revision & t-1       & t-1- t-2  & t-1-t-3   \\
					\hline 
					L.InfExp\_Mean\_ch   &             & -0.295*** & -0.344*** & -0.367*** &               & -0.303*** & -0.348*** & -0.364*** & L.InfExp\_Mean\_ch  &         & -0.433*** & -0.586*** & -0.642*** \\
					&             & (0.034)   & (0.044)   & (0.045)   &               & (0.043)   & (0.059)   & (0.062)   &                    &         & (0.01)     & (0.013)    & (0.025)    \\

@@

	\begin{figure}[p]
		\centering
		\includegraphics[width=0.8\textwidth,totalheight=0.6\textwidth]{figures/inf_shocksQ.png}
			\begin{flushleft}
			{\footnotesize Note: all the shocks are normalized by their sample standard deviation. Technology shock is idetified by long-run restriction of structural VAR with labor productivity, hours and inflation. Oil shock is defined as the max \{0, the largest increase of oil price over the past 12 months.\} }
		\end{flushleft}
		\caption{ Shocks to Inflation}
		\label{Inflationshocks}
	\end{figure}

@@

\begin{figure}[p]
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\caption{Technology and Oil Shocks}
		\includegraphics[width=7cm]{figures/CPIAU_ashocks_nmp_before2007.png}  
		\smallskip
		\includegraphics[width=7cm]{figures/SPFFE_ashocks_nmp_before2007.png} 
		\smallskip
		\includegraphics[width=7cm]{figures/SPFDisg_ab_ashocks_nmp_before2007.png} 
	\end{subfigure}
	\hspace{1em}
	\hfill
	\begin{subfigure}[b]{0.5\textwidth}
		\caption{Monetary Policy Shocks}
		\includegraphics[width=7cm]{figures/CPIAU_ashocks_before2007.png} 
		\smallskip
		\includegraphics[width=7cm]{figures/SPFFE_ashocks_before2007.png} 
		\smallskip
		\includegraphics[width=7cm]{figures/SPFDisg_ab_ashocks_before2007.png} 
	\end{subfigure}
	\caption{Responses of Inflation and Professional Forecast Moments: 1984-2007}
	\label{ReplicateCoibionBefore2007}
\end{figure}

@@

		\begin{figure}[p]
		\begin{subfigure}[b]{0.5\textwidth}
			\centering
			\caption{Technology and Oil Shocks}
			\includegraphics[width=7cm]{figures/Inf_ashocks_nmp.png}  
			\smallskip
			\includegraphics[width=7cm]{figures/SPFFE_ashocks_nmp.png} 
			\smallskip 
			\includegraphics[width=7cm]{figures/SPFDisg_ab_ashocks_nmp.png} 
			\smallskip 
			\includegraphics[width=7cm]{figures/SPFVar_ab_ashocks_nmp.png} 
		\end{subfigure}
		\hfill
		\hspace{1em}
		\begin{subfigure}[b]{0.5\textwidth}
			\caption{Monetary Policy Shocks}
			\includegraphics[width=7cm]{figures/Inf_ashocks.png} 
			\smallskip
			\includegraphics[width=7cm]{figures/SPFFE_ashocks.png} 
			\smallskip
			\includegraphics[width=7cm]{figures/SPFDisg_ab_ashocks.png} 
			\smallskip
			\includegraphics[width=7cm]{figures/SPFVar_ab_ashocks.png} 
		\end{subfigure} 
		\caption{Responses of Inflation and Professional Forecast Moments: 1984-2019}
		\label{ReplicateCoibionwholeperiod}
	\end{figure}

@@

	\begin{figure}[p]

@@

\subsection{Moments matching and parameter estimates (draft in process)}

Table \ref{SMM_Est_SPF} presents the SMM estimates of different model parameters. For each theory, I estimate the theory both in two-steps or jointly using expectation and inflation data. Different rows without each panel reports the estimates by using different sets of moments:forecast errors only,  forecast error and disagreement, and the two plus uncertainty.

\begin{table}[p]
	\caption{SMM Estimates of Different Models: Professionals}
	\label{SMM_Est_SPF}
	\begin{tabular}{lllllll}
		\hline 
		\multicolumn{7}{c}{SE}                            \\
		\hline 
		Moments Used & \multicolumn{1}{c}{2-Step Estimate} & \multicolumn{3}{c}{Joint Estimate}                                                 &            &              \\
			\hline 
		& SE: $\hat\lambda_{SPF}$(Q)          & SE: $\hat\lambda_{SPF}$(Q) & SE: $\rho$                & SE: $\sigma$              &            &              \\
			\hline 
		FE       & 0.47                                & 0.36                       & 1                         & 0.08                      &            &              \\
		FE+Disg      & 0.47                                & 0.38                       & 1                         & 0.1                       &            &              \\
		FE+Disg+Var  & 0.47                                & 0.36                       & 1                         & 0.08                      &            &              \\
			\hline 
		\multicolumn{7}{c}{NI}                                                                                                                                              \\
			\hline 
		Moments Used & \multicolumn{2}{c}{2-Step Estimate}                              & \multicolumn{4}{c}{Joint Estimate}              
		                                  \\
		                                  	\hline 
		& NI: $\hat\sigma_{pb,SPF}$           & $\hat\sigma_{pr,SPF}$      & NI: $\hat\sigma_{pb,SPF}$ & $\hat\sigma_{pr,SPF}$     & NI: $\rho$ & NI: $\sigma$ \\
			\hline 
		FE        & 0.09                                & 2.77                       & 0.093                     & 1.408                     & 0.911      & 0.422        \\
		FE+Disg      & 0.09                                & 2.77                       & 0.093                     & 1.408                     & 0.911      & 0.422        \\
		FE+Disg+Var  & 0.14                                & 3.85                       & 0.133                     & 1.359                     & 0.911      & 0.422        \\
			\hline 
		\multicolumn{7}{c}{DE}                                                                                                                                              \\
			\hline 
		Moments Used & \multicolumn{2}{c}{2-Step Estimate}                              & \multicolumn{4}{c}{Joint Estimate}                                                \\
			\hline 
		& DE: $\theta_{SPF}$                  & DE: $\sigma_{\theta,SPF}$  & DE: $\theta_{SPF}$        & DE: $\sigma_{\theta,SPF}$ & DE: $\rho$ & DE: $\sigma$ \\
			\hline 
		FE       & -0.23                               & 0.22                       & NA                        & NA                        & NA         & NA           \\
		FE+Disg      & -0.26                               & 1.41                       & -0.14                     & 1.44                      & 0.99       & 0.16         \\
		FE+Disg+Var  & -0.24                               & 1.43                       & -0.17                     & 1.44                      & 0.99       & 0.16       \\ 
			\hline 
	\end{tabular}
\end{table}
